The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-08-09 manuscript.Rmd
[fix #47] use iDigBio+OBIS for proportion of species with n records

Environmental conditions are among the primary determinants of species distributions and can thus be used to estimate the response of organisms to climate change. Predictive ecological models forecasting changes in distributions are training on environmental conditions encountered by species in their current distributions. To obtain reliable results, models require at least 10, but ideally 30 or more occurrence records per species [@Wisz2008]. Yet at present, `r prop_10_specimens_species`% of species are represented by $\leq$ 10 records, and `r prop_30_specimens_species`%  by $\leq$ 30 records in iDigBio.

>>>>

Environmental conditions are among the primary determinants of species distributions and can thus be used to estimate the response of organisms to climate change. Predictive ecological models forecasting changes in distributions are training on environmental conditions encountered by species in their current distributions. To obtain reliable results, models require at least 10, but ideally 30 or more occurrence records per species [@Wisz2008]. Yet at present, `r prop_10_specimens_species`% of species are represented by $\leq$ 10 records, and `r prop_30_specimens_species`%  by $\leq$ 30 records based on the combined records in iDigBio and OBIS.
